---
title: "A UN Report on the Relationship between GDP and Life expectancy"
output: html_document
author: "EunGi Kim"
date: "8/3/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_package, include=FALSE}
library(tidyverse)
```

# Introduction
This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r load_data, include=FALSE}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")
```

# Results

## My plot
```{r plot_gdp_lifeexp, echo=FALSE}
ggplot(data=gapminder_1997) +
  aes(x = gdpPercap, y = lifeExp) +
  geom_point()
```

```{r calculate_summary_statistics, include=FALSE}
nCountries <- gapminder_1997 %>%
  select(country) %>%
  n_distinct()

minGDP <- gapminder_1997 %>%
  summarise(round(min(gdpPercap)))

maxGDP <- gapminder_1997 %>%
  summarise(round(max(gdpPercap)))
```

For this analysis, `r nCountries` countries were analyzed for this report. The minimum GDP per capita was `r minGDP`, the maximum GDP per capita was `r maxGDP`.

| Indicator  |  Value |
|---|---|
| Minimum GDP  |`r minGDP`   |
| Mean GDP | |
| Maximum GDP  |`r maxGDP`   |

```{r make_table_with_kable, echo=FALSE}
gapminder_1997 %>%
  filter(continent == "Oceania") %>%
  knitr::kable()
```

bullet point list with 3 items (bold, italics, both)
turn into numbered list
add a hyperlinked url

1. **R**
1. *ggplot*
1. ___bold italics___
1. [Cheatsheet for Markdown](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)


